Effects of the body force on the pedestrian and evacuation dynamics

### 2020-02-06 paper.tex
algunas correcciones de signos
correcciones menores de gramatica en la parte de bottleneck

The sliding friction reduction appears as the fist feature for enhancing
the overall evacuation performance. Either reducing the mean overlap and the mean degree
tend to diminish the mean sliding 
friction within the crowd. 
Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex 
phenomenon. We will focus on this issue in an upcoming investigation.\\

@@

We may summarize this Section as follows. We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation. This is similar to explore the unitless space $(\mathcal{A},\mathcal{K}_c)$. Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern. Stiffness affects either the presence of the blocking clusters and the pedestrians overlap. The less they compress, the less intense becomes the sliding friction among them. Additionally, the fewer the blocking clusters the easier they get out. \\

@@

\begin{equation}
S = \frac{<v_x(center)> - <v_x(boundary)> }{\left | y(center) - y(boundary) \right |} 
\end{equation}

Where $<>$ means the average taken over time. By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center). As the stiffness level increases, the crowd becomes less deformable. This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate decreases with $k_n$. \\

>>>>

The sliding friction reduction appears as the first feature for enhancing
the overall evacuation performance. Either reducing the mean overlap and the mean degree
tend to diminish the mean sliding 
friction within the crowd. 
Notice, however, that switching from a FIS regime (positive slope) to a  FIF 
regime (negative slope) in Fig.~\ref{vd_vs_te} appears as a more complex 
phenomenon. We will focus on this issue in an upcoming investigation.\\

@@

We may summarize this Section as follows. We explored the parameter space along $v_d$ and $k_n$ for the bottleneck situation. This is similar to explore the unitless space $(\mathcal{A},\mathcal{K}_c)$. Soft pedestrians attain a FIS or FIS+FIF evacuation pattern but, stiff pedestrians (for any fixed $\mathcal{A}$ value within the explored range) exhibit a single FIF pattern. Stiffness affects either the presence of the blocking clusters and the pedestrians overlap. The less they overlap, the less intense becomes the sliding friction among them. Additionally, the fewer the blocking clusters the easier they get out. \\

@@

\begin{equation}
S = \frac{\langle v_x(center)\rangle - \langle v_x(boundary)\rangle }{\left | y(center) - y(boundary) \right |} 
\end{equation}

Where $\langle \rangle$ means the average taken over time. By this definition we compare the velocity of the pedestrians close to the wall (boundary) with respect to the velocity of the pedestrians in the center of the corridor (center). As the stiffness level increases, the crowd becomes less deformable. This phenomenon is shown in Fig.~\ref{strain_rate_vs_kn} where we can see that the strain rate decreases with $k_n$. \\
